Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Good solution re-written

Good Technology is a company that was founded in 1996 in California. The philosophy followed by Good is similar to Samsung's Knox one: to create a secure container that places an unreachable partition between personal and business data in order to protect company's assets. The solutions that they offer \cite{Good_tool} are similar than the previous ones. They have focused in mobile (not laptops) devices, though they support a different of Operating Systems (OSs), and in separating personal and company data. A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, PIM, calendar), intranet, and in-house or third-party mobile applications. Finally, Good offers best practise recommendations to help the company's BYOD policies such as reimbursements and stipends. There is a document available at Good's webpage\footnote{\url{http://www1.good.com/mobility-management-solutions/bring-your-own-device}} which contains several questions about Information Security Policies and how to cope with all of them.

>>>>

The philosophy followed by Good is similar to Samsung KNOX one: to create a secure container that places an unreachable partition between personal and business data in order to protect company assets. The solutions that they offer \cite{Good_tool} are similar than in the already described solutions. Their solution has been developed for the main Operating Systems (OSs) (iOS, Android, and Windows phone), and also desktop computers with Windows. A Good's secure Network Operations Center (NOC) is introduced for dealing with the unauthorised devices, or for providing access to secure collaboration solutions (email, documents, calendar), the intranet, and both in-house or third-party mobile applications. Finally, Good offers best practise recommendations to help the company developing BYOD policies. A document can be accessed from Good's webpage \cite{Good_tool}, which contains several questions about ISPs and how to cope with all of them.
